---
title: "BREWERY ANALYSIS"
author: "Casey Martinez & Asha Saxena"
date: "October 18, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = 'C:\\Users\\Casiano\\Documents\\SMU Data Science\\SMU\\Case Study 1')
```
## GOALS & OBJECTIVES

Project Goal is to identify an apparent relationship between the bitterness of the beer and its alcoholic content. 

Objective of the project is to analyze the following:
  1) The beer and brewery data set 
  2) By State
  3) By Alcoholic Content (ABV)
  4) By Bitterness Level(IBU)
  

## SCOPE & PHASES

Scope of this project is as follows:
  1) Analyzing the data set provided for breweries and beer in United States
  2) Cleaning the Data
  3) Computing the data set 
  4) Evaluating the statistical results
  5) Conclusion 


## PHASE 1: ANALYZING THE DATA
```{r,echo=TRUE}
library(ggplot2)
library(data.table)
library(dplyr)
library(ggthemes)

source('Analysis/makefile.R')
```
### Q1. How many breweries are present in each state?

We found the data set contains 50 states in additon to Washington DC. 
```{r,echo=TRUE,fig.width=15,fig.height=5}
#question 1
q1 <- brew %>% group_by(brew$State) %>% summarize(TotalBreweries = n())
q1 <- as.data.frame(q1)

q1_plot <- ggplot(data = q1, aes(x = as.factor(q1$`brew$State`),y = TotalBreweries)) + 
  geom_col(color = 'red',fill = 'pink') +
  labs(y = 'N',x = "State") +
  ggtitle('Total Number of Breweries per State') +
  theme_economist()

print(q1_plot)

```

### Q2. Merge beer data with the breweries data. Print the first Six observations and the last six observations to check the merged file.

We then merged the beer and breweries data set and print the first six and the last six observations to confirm the merged file.


## PHASE 2: DATA CLEANZING
```{r,echo=TRUE}
#Question 2
head(merged_data, 6)
tail(merged_data, 6)
```
### Q3. Report the number of NA's in each column.

First step in cleaning the data is to remove the null values. 
```{r,echo=TRUE}
q3a <- sum(is.na(merged_data$ABV))
q3b <- sum(is.na(merged_data$IBU))
print(q3a)
print(q3b)
```

## PHASE 3: COMPUTATION 

### Q4. Compute the median alcohol content and international bitterness unit for each state. Plot a bar chart to compare.

After merging and cleaning the data, we looked at the median alcohol content and international bitterness unit for each state.

Please see attached the bar chart to compare.

```{r,echo=TRUE,fig.width=15,fig.height=5}

#question4
q4 <- merged_data %>% group_by(merged_data$State) %>% summarize(median_ABV = median(ABV), median_IBU = median(IBU))
q4 <- as.data.frame(q4)
setnames(q4, "merged_data$State", "State")

#bar chart for median_ABV
q4a <- ggplot(data = q4, aes(x = State,y = median_ABV)) + 
  geom_col(color = 'red',fill = 'pink') +
  labs(y = 'Median ABV',title = 'Median Alcohol Content') +
  theme_economist()
               
#bar chart for median_IBU
q4b <- ggplot(data = q4, aes(x = State,y = median_IBU)) + 
  geom_col(color = 'red',fill = 'pink') +
  labs(y = 'Median IBU',title = 'Median International Bitterness Content') +
  theme_economist()                 

print(q4a)
print(q4b)
```


### Q5. Which state has the maximum alcoholic (ABV) beer? Which state has the most bitter (IBU) beer?

We then looked at the data for state has the maximum alcoholic (ABV) beer and the state that has the most bitter (IBU) beer.

We found the following:

**State has the maximum alcoholic (ABV) beer: Colorado (CO)**
**State has themostbitter (IBU) beer: Missouri (MO)**


## PHASE 4: EVALUATING STATISTICAL RESULTS

### Q6. Summary statistics for the ABV variable.
```{r,echo=TRUE}
#question 6
q6 <- summary(merged_data$ABV)
print(q6)
```


## PHASE 5: CONCLUSION

### Q7. Is there an apparent relationship between the bitterness of the beer and its alcoholic content? Draw a scatter plot.

We see here is a linear relationship between the bitterness of the beer and its alcoholic content.
```{r,echo=TRUE,fig.width=15,fig.height=5}
#scatter plot
q7 <- ggplot(data = merged_data, aes(x = ABV,y = IBU)) + 
  geom_point() +
  labs(x = 'ABV', y = 'IBU',title = 'International Bitterness Content vs. Alcoholic Content') +
  theme_economist() +
  geom_smooth(method = 'lm')
  
print(q7)  

#linear reegression model
q7model <- lm(IBU ~ ABV, merged_data)
summary(q7model)
```


