---
title: "Assignment4Q1"
author: "Asha Saxena"
date: "September 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Q1.a. Navigate on GitHub to https://github.com/rudeboybert/fivethirtyeight and read README.md.Install the fivethirtyeight package.

    install.packages("fivethirtyeight")

### Output Q1.a
    Installing package into 'C:/Users/ashas/Documents/R/win-library/3.3'
    (as 'lib' is unspecified)
    trying URL 'https://cran.rstudio.com/bin/windows/contrib/3.3/fivethirtyeight_0.3.0.zip'
    Content type 'application/zip' length 4398780 bytes (4.2 MB)
    downloaded 4.2 MB

    package 'fivethirtyeight' successfully unpacked and MD5 sums checked

    The downloaded binary packages are in
	    C:\Users\ashas\AppData\Local\Temp\RtmpaU4pWl\downloaded_packages


## Q1.b In the listing of Data sets in package 'fivethirtyeight,' assign the eighteenth data set to an object 'df.'

### eighteenth data set <- college_recent_grads
    

```{r , echo=TRUE}
library(fivethirtyeight)
data(package = "fivethirtyeight") 
df<-data.frame(college_recent_grads)
    class(df)
```

## Q1.c. Use a more detailed list of the data sets to write out the URL in a comment to the related news story.

```{r, ECHO=TRUE}
 head(df)
```

### Output fo 1c.
# A tibble: 6 x 22
    major_code                                  major
           <int>                                  <chr>
    1       5601                  Construction Services
    2       6004      Commercial Art And Graphic Design
    3       6211                 Hospitality Management
    4       2201 Cosmetology Services And Culinary Arts
    5       2001             Communication Technologies
    6       3201                        Court Reporting
      # ... with 20 more variables: major_category <chr>,
      #   grad_total <int>, grad_sample_size <int>,
      #   grad_employed <int>,
      #   grad_employed_fulltime_yearround <int>,
      #   grad_unemployed <int>, grad_unemployment_rate <dbl>,
      #   grad_p25th <dbl>, grad_median <dbl>,
      #   grad_p75th <int>, nongrad_total <int>,
      #   nongrad_employed <int>,
      #   nongrad_employed_fulltime_yearround <int>,
      #   nongrad_unemployed <int>,
      #   nongrad_unemployment_rate <dbl>,
      #   nongrad_p25th <dbl>, nongrad_median <dbl>,
      #   nongrad_p75th <dbl>, grad_share <dbl>,
      #   grad_premium <dbl>
  
## Q1.d. Using R command(s), give the dimensions and column names of this data frame.
    
    dim(college_grad_students)
    
### Output of 1d.
```{r, ECHO=TRUE}
dim(college_grad_students)
```

    [1] 173  21
    
### Column names of this data frame
    
     colnames(college_grad_students)
    
### Output for column name.
```{r, ECHO=TRUE}
colnames(college_grad_students)
```

    [1] "major_code"                          "major"                               "major_category"                   
    [4] "grad_total"                          "grad_sample_size"                    "grad_employed"                   
    [7] "grad_employed_fulltime_yearround"    "grad_unemployed"                     "grad_unemployment_rate"          
    [10] "grad_p25th"                          "grad_median"                         "grad_p75th"                     
    [13] "nongrad_total"                       "nongrad_employed"                 "nongrad_employed_fulltime_yearround"
    [16] "nongrad_unemployed"                  "nongrad_unemployment_rate"           "nongrad_p25th"              
    [19] "nongrad_median"                      "nongrad_p75th"                       "grad_share"             
    [22] "grad_premium"                       

    
## Q2a. Write an R command that gives you the column names of the data frame. Right after that, write one that counts the number of columns but not rows.

    ncol(college_recent_grads)
```{r, ECHO=TRUE}
ncol(college_recent_grads)
```

    
### Output for 2a.

    [1] 21
    
## 2b. Generate a count of each unique major_category in the data frame.This should look like a matrix or data frame containing the major_category and the frequency it occurs in the dataset. Assign it to major_count.

    major_count <- (df$major_category)
    count(major_count)
```{r, ECHO=TRUE}
library("plyr")
    major_count <- (df$major_category)
    count(major_count)
```

### Output of 2b.
                                             x freq
    1      Agriculture & Natural Resources   10
    2                                 Arts    8
    3               Biology & Life Science   14
    4                             Business   13
    5          Communications & Journalism    4
    6              Computers & Mathematics   11
    7                            Education   16
    8                          Engineering   29
    9                               Health   12
    10           Humanities & Liberal Arts   15
    11 Industrial Arts & Consumer Services    7
    12                   Interdisciplinary    1
    13                 Law & Public Policy    5
    14                   Physical Sciences   10
    15            Psychology & Social Work    9
    16                      Social Science    9
 
## 2c. Make a barplot of major_count

    library("plyr")
    MajorCountBarPlot <- count(major_count)
    count(major_count)
    barplot(MajorCountBarPlot$freq, horiz = TRUE, col = 'green', names= MajorCountBarPlot$x, xlim=c(0,30), xlab =     "Major Category", main = 'Majors by Major Category')

### Output for 2c.

library("plyr")
MajorCountBarPlot <- count(major_count)
count(major_count)
barplot(MajorCountBarPlot$freq, horiz = TRUE, col = 'green', names= MajorCountBarPlot$x, xlim=c(0,30), xlab =     "Major Category", main = 'Majors by Major Category')  


```{r, ECHO=TRUE}
library("plyr")
MajorCountBarPlot <- count(major_count)
count(major_count)
par(las=2)
barplot(MajorCountBarPlot$freq, horiz = TRUE, col = 'green', names= MajorCountBarPlot$x, xlim=c(0,30), xlab =     "Major Category", main = 'Majors by Major Category')  
```


## 2d. Write the fivethirtyeight data to a csv file.

```{r, ECHO=TRUE}
write.csv(df, file = "fivethirtyeight.csv",row.names=FALSE)
```

## 3a. Start a new repository on GitHub for your SMU MSDS homework.Add whatever you would like to this repo.

    https://github.com/ashasaxena/SMU
    
## 3b. Create a README.md file which explains the purpose of the repository

    https://github.com/ashasaxena/SMU/blob/master/Assignment04/README.md
    
## 3c. In one (or more) of the nested directories, post your RMarkdown script, HTML file,and data from 'fivethirtyeight.'

    https://github.com/ashasaxena/SMU/tree/master/Assignment04
    
### Make sure that in your README or elsewhere that you credit fivethirtyeight in some way. 
    
    https://github.com/ashasaxena/SMU/blob/master/Assignment04/README.md
    
## 3d. In your RMarkdown script, please provide the link to this GitHub so the grader can see it.

    See above.
    
